# NA Values

```{r}
library(tidyverse)

# df <- tibble(x = c(1, NA, 3))

df <- tibble(x = c(1, NA, 3),
             y = c(4, NA, NA),
             z = c(6, 7, 8))
```

## Replacing NA Values

Replacing NA values in a dataframe is simple.

You can place the `replace_na()` function inside of mutate:

```{r}
df %>%
  mutate(x = replace_na(x, 0))
```

And using scoped verbs:

```{r}
df %>%
  mutate_all(~replace_na(., "Unknown"))
```

Or you can specify variables wrapped inside `list()`:

```{r}
df %>% replace_na(list(x = 0, y = "unknown"))
```

## Assigning NA Values

Sometimes you most to convert values to `NA` manually. Here we have `NA` values stored as a word vector "NA". (Be sure to see options for automatically converting NA values when you import data here.) For these tasks, `dplyr::na_f()` is is particularly useful wrapped inside of `mutate()`, as it is meant to work on vectors rather than entire data frames. 

```{r}
df <- tibble(x = c(1, NA, 3),
             y = c("dog", "NA", "NA"),
             z = c(6, "NA", 8))

df
```

```{r}
df %>%
  mutate(y = na_if(y, "NA"))
```

As before, you can easily scope it:

```{r}
df %>%
  mutate_all(~na_if(., "NA"))
```

What if you have multiple different values? For example, imagine you have columns which contain a dash for certain NA values and a literal character string `"NA"` for others.

```{r}
df <- tibble(x = c(1, NA, 3),
             y = c("dog", "NA", "NA"),
             z = c(6, "-", 8))

df
```

This is a bit tricky (you can read why [here](https://github.com/tidyverse/dplyr/issues/1972)). At the moment there are several options:

* Manually convert each column.
* Create a custom function.
* Replace a selection of known NA value representations and then use `na_if()`.
* The [naniar](https://github.com/njtierney/naniar) package.

More on this later.

#### The naniar Package

```{r}
library(naniar)

df %>% replace_with_na(replace = list(y = "NA"))
```

```{r}
df %>%
  naniar::replace_with_na_all(condition = ~.x %in% c("NA", "-"))
```

## Using `filter()` with NA Values

`filter()` will only include rows where the condition evaluates to `TRUE` and thus excludes `NA` values present in your data. This is problematic because often `NA` values are important. If you wish to return `NA` values, ask for them explicitly.

```{r}
# This will exclude NA values
filter(df, x > 1)

# Now include NA
filter(df, is.na(x) | x > 1)
```

## Dropping NA Values

* Drop rows with NA vlaues with [`tidyr::drop_na()`](https://tidyr.tidyverse.org/reference/drop_na.html).
* `drop_na()` supports scoping.

Example from the official documentation:

```{r}
library(dplyr)
df <- tibble(x = c(1, 2, NA), y = c("a", NA, "b"))
df %>% drop_na()
df %>% drop_na(x)
```

You can also use base R's `na.omit()` wrapped inside of `filter()`:

```{r}
df %>% filter(!is.na(x))
```
