# Data Export

## Writing Multiple File to Disk

I like to save binary file types to disk, specifically `.csv` files.

```{r}
library(purrr)
library(gapminder)

gapminder <- gapminder %>%
  filter(country %in% c("United States", "Canada", "Mexico"))

gapminder %>%
    nest(-country) %>%
    pwalk(~write_csv(x = .y, path = paste0(.x, ".csv")))
```

In the code above:

* `.y` is the column containing the individual data frames of each country. It is the data which will be passed to the first argument of `read_csv()`. 
* `.x` will be the first column containing the country name, it we will use it to construct the system path for where the `.csv` file will be saved.

## Cleaning Things Up

In the code above we used the first data column as our indexing term for the `.csv` files. While this is quick and effective, there are several problems with the approach:

* We lose the data column when nesting.
* The names of the countries are not consistently formatted. For example, they have varying case use and there are spaces present in the names (e.g., "United States"). What to do?

I often find it useful to create indexing values. For this dataset, it's as simple as removing the case and replacing the gaps with a separation chracter such as an under (`_`) or a dash (`-`).

```{r}
gapminder %>%
  mutate(id = paste)
```

