# `case_when()`

The `case_when()` function is a generalization of `if_else()`. Use `case_when()` if you find yourself needing multiple `if_else()` statements.

```{r}
library(tidyverse)
library(gapminder)
```

This example is from the [official documention](https://dplyr.tidyverse.org/reference/case_when.html):

```{r}
starwars %>%
  select(name:mass, gender, species) %>%
  mutate(
    type = case_when(
      height > 200 | mass > 200 ~ "large",
      species == "Droid"        ~ "robot",
      TRUE                      ~ "other"
    )
  )
```

## Using `case_when()` With Text Data

You can use `case_when()` to create new variables based on the presence of certain strings. You can combine it with `str_detect()` or base R's `grepl()`.

```{r}

```

## Wrapping `case_when()` Inside Functions

Keep in mind that `case_when()` is not a tidy eval function. "If you'd like to reuse the same patterns, extract the `case_when()` call in a normal function:"

## Using `case_when()` With NA Values

### NA as a Condition

```{r}
df <- tibble(x = c(1, NA, 3),
             y = c("dog", NA, NA))

df
```

```{r}
df %>%
  mutate(
    status = case_when(
      is.na(x) ~ "Unknown",
      TRUE ~ "Complete"
  ))
```

### Converting to NA

You must be very precise with type delcaration when dealing with `NA` values with `case_when()`. `NA` is of type logical, but if you are using `case_when()` to recode you must use the right sorts or you will get an error. The types include:

* `NA_real_`
* `NA_character_`
* `NA_integer_`
* `NA_complex_`

Here an error will be thrown:

```{r, eval=FALSE}
iris %>% mutate(
  Sepal.Width = case_when(
    Sepal.Length == 5.1 ~ NA,
    TRUE ~ 2)) %>% head
```

But when we are type-specific:

```{r}
iris %>% mutate(
  Sepal.Width = case_when(
    Sepal.Length == 5.1 ~ NA_real_,
    TRUE ~ 2)) %>% head
```

