# Data Manipulation

```{r, echo=FALSE}}
library(tidyverse)
```

## Ideas

* **Tidyverse Mechanics** - This section will discuss certain mechanics of using tidyverse packages.
  * Tibbles
  * Row-wise operations
  * Col-wise operations

## Workhorse Packages

The workhorse packages of the tidyverse are **tidyr** and **dplyr**. In general, we use **tidyr** for *reshaping* the overall structure of data and we use **dplyr** to *manipulate* it. I say "in general" because some functions from tidyr may seem like they are manipulation tasks, and some form dpylr may seem like they are reshaping tasks.

## Outline of the Chapter

* **PART - tidyr**
  * Pivoting
    * pivot_longer
    * pivot_wider
  * Separating and Uniting Columns
    * separate
    * unite
  * Separating Rows
    * separate_rows
  * Nesting Data
    * nest
  * Unnesting Data 

* **PART dplyr**
  * Recoding
    * if_else
    * case_when

* **PART - tidyverse Extras**
  * Scoped Verbs
  * Tibbles
  * The Pipe

* Converting Nested Lists Into Tibbles - https://tidyr.tidyverse.org/articles/rectangle.html



*Personal organization only...*

## Reshaping with `tidyr`

We reshape data with `pivot_wider()` and `pivot_longer()`.

### `pivot_longer()`

[`pivot_longer()` Offical Documentation](https://tidyr.tidyverse.org/reference/pivot_longer.html)

We use `pivot_longer()` when we want to go from a "wide" to a "longer" dataset. In more formal words, we use this function where we have columns that in fact should not be columns and instead be different levels of a factor variable. This is common if much of your exposure to datawork has been in spreadsheets. Sometimes this is obvious, sometimes not.

```{r}
head(relig_income)
```

```{r}
relig_income %>%
  pivot_longer(-religion, names_to = "income", values_to = "count") %>%
  head()
```

#### Complex `pivot_longer()` Operations

```{r}
billboard %>%
 pivot_longer(
   cols = starts_with("wk"),
   names_to = "week",
   names_prefix = "wk",
   values_to = "rank",
   values_drop_na = TRUE
 )
```
